Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-31 analysis/paper/hotspots-paper.Rmd
added back github_document output format
switched eval -> TRUE for Chr5 & 7 hotspots
set outputs to do html_document2 AFTER github_document; also set github_document with html_preview: false

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "7/27/2019"
bibliography: research.bib
linkReferences: true
link-citations: true
output: bookdown::html_document2
---

>>>>

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "7/27/2019"
bibliography: research.bib
linkReferences: true
link-citations: true
output: 
  - github_document:
      html_preview: false
      toc: true
      toc_depth: 3
  - bookdown::html_document2  
---
